Extending the Advanced Forensic Format to accommodate Multiple Data Sources, Logical Evidence, Arbitrary Information and Forensic Workflow

### 2009-03-14 paper/paper.tex
Added patches for the afflib patch.

In recent years there has been a steady and growing interest in the
actual file formats and containers used to store this digital
evidence. Early practitioners created exact bit-for-bit copies
(``mirror disks'') employed proprietary software systems
(e.g. \cite{safeback,ilook,encase}) for making and authenticating
``images'' of digital evidence. PyFlag\cite{pyflag} introduced a
``seekable gzip'' format that allowed disk images to be stored in a
form that was compressed but allowed the random-access to evidence
data necessary for forensic analysis. The \emph{sgzip} format does not
store any metadata at all.

@@

The AFF4 metadata model described in this work, is based on (subject,
property, value) statements. An explicitly defined subject (identified
by an AFF4 URN) allows one to not only associate traditional EWF style
metadata with a contained image, but to also define new information
entities representing both real world and virtual entities related to
the matter. For example, an AFF4 compliant hard disk acquisition tool
should, in addition to storing an image, store entities representing
and describing the tool itself, the operator of the tool, the user
supplied parameters supplied to the tool, and the drive being imaged.

@@

>>>>

\subsection{Prior Work}
In recent years there has been a steady and growing interest in the
actual file formats and containers used to store this digital
evidence. Early practitioners created exact bit-for-bit copies
(``mirror disks'') employed proprietary software systems
(e.g. \cite{safeback,ilook,encase}) for making and authenticating
``images'' of digital evidence. PyFlag\cite{pyflag} introduced a
``seekable gzip'' format that allowed disk images to be stored in a
form that was compressed but allowed the random-access to evidence
data necessary for forensic analysis. The \emph{sgzip} format does not
store any metadata at all.

@@

@@

\subsection{This paper}
The AFF4 metadata model described in this work, is based on (subject,
property, value) statements. An explicitly defined subject (identified
by an AFF4 URN) allows one to not only associate traditional EWF style
metadata with a contained image, but to also define new information
entities representing both real world and virtual entities related to
the matter. For example, an AFF4 compliant hard disk acquisition tool
should, in addition to storing an image, store entities representing
and describing the tool itself, the operator of the tool, the user
supplied parameters supplied to the tool, and the drive being imaged.
